Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-08-17 Ben_Manuscripts/structure_paper/Draft.tex

  Adding water to the system appears to promote the appearance of R-double,
  through the creation of hydrogen bonding of water to carboxylate groups of
  consecutive layers. We added water to the parallel displaced and sandwiched
  configurations in the ordered basin and equilibrated them according to the wet
  equilibration procedure. There is no experimental measurement of water
  concentration in these membranes so we tested a range of water concentrations
  from 1\% to 5\%. R-double appears transiently in the simulated XRD pattern of
  the parallel displaced configuration with 1 wt\% water (Figure
  \ref{fig:solvated_pore_rzplot_norestraints}). It is not initially present, but
  appears after 200 ns of simulation time. After 450 ns, it disappears again.
  Simulated XRD patterns of all other solvated systems tested are shown in Figure
  S~\ref{S-fig:solvation}, however R-double is not present.

>>>>

  The addition of water to the system appears to promote the appearance of R-double.
#  through the creation of shared hydrogen bonds between water molecules and carboxylate
#  groups of vertically stacked monomers. 
  We added water to the parallel displaced and sandwiched
  configurations in the ordered basin and equilibrated them according to the wet
  equilibration procedure. There is no experimental measurement of water
  concentration in these membranes so we tested a range of water concentrations
  from 1\% to 5\%. R-double appears transiently in the simulated XRD pattern of
  the parallel displaced configuration with 1 wt\% water (Figure
  \ref{fig:solvated_pore_rzplot_norestraints}). It is not initially present, but
  appears after 200 ns of simulation time. After 450 ns, it disappears again.
  Simulated XRD patterns of all other solvated systems tested are shown in Figure
  S~\ref{S-fig:solvation}, however R-double is not present.
